Measuring efficiency of the greedy-like heuristics for solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization

### 2020-10-08 doc/paper.tex
update
some results added

      After conducting preliminary results, we decided to use the following parameters for our algorithms:
      \begin{itemize}
        \item \textsc{Greedy + Cplex} parameters: $K = 0.05 \cdot n$. 
      \end{itemize}
     The benchmark sets and the executable file of our software for this project are provided at \href{link}{link}.
	\subsection{Results and Discussion}
        The following algorithms are included in our computation:
        \begin{itemize}
        	\item  exact approaches: CP and ILP approach.The later is, henceforth, called \textsc{Cplex};
        \end{itemize}  and 6 heuristic approaches: 
           \begin{itemize}
           	\item three pure greedy methods, guided by $g_1$, $g_2$ and $g_3$ greedy criterion. We label them by \textsc{Greedy-1}, \textsc{Greedy-2} and \textsc{Greedy-3}, respectively;
            %\item three \textsc{Greedy+Shaking} variants, henceforth labeled by \textsc{Greedy}-$i$+Shaking, $i=1,2,3$, where $i$ stands for heuristic $g_i$ involved in the method;
            \item three \textsc{Greedy+Cplex} variants, henceforth labeled by  \textsc{Greedy}-$i$+\textsc{Cplex}, $i=1,2,3$, 
            where $i$ stands for heuristic $g_i$ involved as the greedy criterion of the hybrid;
           \end{itemize}
         Summarized numerical results for all of our algorithm variants are displayed in Table~\ref{tab:t_w0} and Table~\ref{tab:t_w1} for topollogically-based benchmarks and point-based benchmarks, respectively.

         \begin{table}
         \centering
         \begin{tabular}{ |p{4cm}|p{1.5cm}p{1cm}|p{1.5cm} p{1cm} |  }
         	\hline
         	\multicolumn{5}{|c|}{Avg. results on the topollogically-based benchmarks.} \\
         	\hline
            \multicolumn{1}{|c|}{}&
            \multicolumn{2}{|c|}{$Small$}&
            \multicolumn{2}{|c|}{$Large$} \\
            \hline	
         	Algorithm  & $|\bar{s}|$ & $\bar{\sigma}$ & $|\bar{s}|$ & $\bar{\sigma}$  \\ \hline \hline
            \textsc{Cplex} & & & & \\ \hline
            \textsc{Cp} & & & & \\ \hline
         	\textsc{Greeedy-1} & & & & \\ \hline
         	\textsc{Greeedy-2} & & & & \\ \hline
         	\textsc{Greeedy-3} & & & & \\ \hline
         	\textsc{Greeedy-1 + Cplex} & & & & \\ \hline
         	\textsc{Greeedy-2 + Cplex} & & & & \\ \hline
         	\textsc{Greeedy-3 + Cplex} & & & & \\ \hline
         	\hline
         \end{tabular}
         \caption{Different combinations of the algorithms.}
        \end{table}

       \begin{table}
    	\centering
    	\begin{tabular}{ |p{4cm}|p{1.5cm}p{1cm}|p{1.5cm} p{1cm} |  }
    		\hline
    		\multicolumn{5}{|c|}{Avg. results on the point-based benchmarks.} \\
    		\hline
    		\multicolumn{1}{|c|}{}&
    		\multicolumn{2}{|c|}{$Small$}&
    		\multicolumn{2}{|c|}{$Large$} \\
    		\hline	
    		Algorithm  & $|\bar{s}|$ & $\bar{\sigma}$ & $|\bar{s}|$ & $\bar{\sigma}$  \\ \hline \hline
    		\textsc{Cplex} & & & & \\ \hline
    		\textsc{Cp} & & & & \\ \hline
    		\textsc{Greeedy-1} & & & & \\ \hline
    		\textsc{Greeedy-2} & & & & \\ \hline
    		\textsc{Greeedy-3} & & & & \\ \hline
    		\textsc{Greeedy-1 + Cplex} & & & & \\ \hline
    		\textsc{Greeedy-2 + Cplex} & & & & \\ \hline
    		\textsc{Greeedy-3 + Cplex} & & & & \\ \hline
    		\hline
    	\end{tabular}
    	\caption{Different combinations of the algorithms.}
    \end{table}

>>>>

      After conducting preliminary results, we decided to use the following parameters for our algorithms:
      \begin{itemize}
        \item \textsc{Greedy + Cplex} parameters: $K = 0.05 \cdot n$. 
      \end{itemize}
     The benchmark sets and the executable file of our software for this project are provided at \href{link}{link}.
	\subsection{Results and Discussion}
        The following algorithms are included in our computation:
        \begin{itemize}
        	\item  exact approaches: CP and ILP approach.The later is, henceforth, called \textsc{Cplex};
        \end{itemize}  and 6 heuristic approaches: 
           \begin{itemize}
           	\item three pure greedy methods, guided by $g_1$, $g_2$ and $g_3$ greedy criterion. We label them by \textsc{Greedy-1}, \textsc{Greedy-2} and \textsc{Greedy-3}, respectively;
            %\item three \textsc{Greedy+Shaking} variants, henceforth labeled by \textsc{Greedy}-$i$+Shaking, $i=1,2,3$, where $i$ stands for heuristic $g_i$ involved in the method;
            \item three \textsc{Greedy+Cplex} variants, henceforth labeled by  \textsc{Greedy}-$i$+\textsc{Cplex}, $i=1,2,3$, 
            where $i$ stands for heuristic $g_i$ involved as the greedy criterion of the hybrid;
           \end{itemize}
         From our results, we noticed that there is no significant difference between the results of \textsc{Greedy-2} and \textsc{Greedy-3}. Therefore, we report only the results of \textsc{Greedy-2} algorithm.
         Summarized numerical results for all of our algorithm variants are displayed in Table~\ref{tab:t_w0} and Table~\ref{tab:t_w1} for topollogically-based benchmarks and point-based benchmarks, respectively.

         \begin{table}
         \centering
         \begin{tabular}{ |p{4cm}|p{1.5cm}p{1cm}|p{1.5cm} p{1cm} |  }
         	\hline
         	\multicolumn{5}{|c|}{Avg. results on the topollogically-based benchmarks.} \\
         	\hline
            \multicolumn{1}{|c|}{}&
            \multicolumn{2}{|c|}{$Small$}&
            \multicolumn{2}{|c|}{$Large$} \\
            \hline	
         	Algorithm  & $|\bar{s}|$ & $\bar{\sigma}$ & $|\bar{s}|$ & $\bar{\sigma}$  \\ \hline \hline
            \textsc{Cplex} & 15.93 & 0.0 & & \\ \hline
            \textsc{Cp} &  16.04 & 0.0 & & \\ \hline
         	\textsc{Greeedy-1} & 22.04  & & & \\ \hline
         	\textsc{Greeedy-2} & 19.97  & & & \\ \hline
         	\textsc{Greeedy-1 + Cplex} & 18.49 & & & \\ \hline
         	\textsc{Greeedy-2 + Cplex} & 18.39 & & & \\ \hline

         	\hline
         \end{tabular}
         \caption{Different combinations of the algorithms.}
        \end{table}

       \begin{table}
    	\centering
    	\begin{tabular}{ |p{4cm}|p{1.5cm}p{1cm}|p{1.5cm} p{1cm} |  }
    		\hline
    		\multicolumn{5}{|c|}{Avg. results on the point-based benchmarks.} \\
    		\hline
    		\multicolumn{1}{|c|}{}&
    		\multicolumn{2}{|c|}{$Small$}&
    		\multicolumn{2}{|c|}{$Large$} \\
    		\hline	
    		Algorithm  & $|\bar{s}|$ & $\bar{\sigma}$ & $|\bar{s}|$ & $\bar{\sigma}$  \\ \hline \hline
    		\textsc{Cplex} & & & & \\ \hline
    		\textsc{Cp} & & & & \\ \hline
    		\textsc{Greeedy-1} & & & & \\ \hline
    		\textsc{Greeedy-2} & & & & \\ \hline

    		\textsc{Greeedy-1 + Cplex} & & & & \\ \hline
    		\textsc{Greeedy-2 + Cplex} & & & & \\ \hline

    		\hline
    	\end{tabular}
    	\caption{Different combinations of the algorithms.}
    \end{table}
        From the numerical results, we observe the following conclusions:
        \begin{itemize}
        	\item \fxnote{TODO}
        \end{itemize}
